Software Citation Principles

### 2016-02-23 sc-principles/software-citation-principles.tex
Oxfordizing a comma (oxfordising?)

With close to 50 working group participants representing a range of research domains, the working group was tasked to
document existing practices in their respective communities. A total of 47 documents were submitted by working group
participants with the life sciences, astrophysics and geosciences being particularly well-represented in the submitted
resources.

>>>>

With close to 50 working group participants representing a range of research domains, the working group was tasked to
document existing practices in their respective communities. A total of 47 documents were submitted by working group
participants with the life sciences, astrophysics, and geosciences being particularly well-represented in the submitted
resources.
